\textbf{Estimating the proportion of beneficial mutations that are not adaptive in mammals}

### 2024-12-06 manuscript/main-PLOS-revision-2-plos2015.tex
Technical check requests

\section*{Acknowledgements}
\label{sec:acknowledgment}
We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
This work was performed using the computing facilities of the CC LBBE/PRABI\@.
This study makes use of data generated by the NextGen Consortium.
Funding:
Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.

\section*{Competing interests}
The authors declare no conflicts of interest.

>>>>

\section*{Acknowledgements}
\label{sec:acknowledgment}
We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
This work was performed using the computing facilities of the CC LBBE/PRABI\@.
This study makes use of data generated by the NextGen Consortium.

\section*{Funding}
This work was funded by Faculté de Biologie et de Médecine, Université de Lausanne (https://www.unil.ch; to TL, DAH and NS) and Agence Nationale de la Recherche (https://anr.fr/; grant ANR-19-CE12-0019 / HotRec to JJ). The funders did not play any role in the study design, data collection and analysis, decision to publish, or preparation of the manuscript.

\section*{Competing interests}
The authors have declared that no competing interests exist.
